SNIK Quiz: A Multiple Choice Game about Information Management in Hospitals

### 2022-03-17 paper.tex
Resolve #1: Finish submission. Get down to 5 pages.

\begin{abstract}
SNIK is a knowledge base about the management of health information systems generated by extracting Linked Data from textbooks and other sources.
SNIK describes health information management functions, roles executing these functions, and entity types, the information used or updated by these functions.
We present SNIK Quiz, a browser game in which students answer multiple-choice questions about information management in hospitals based on SNIK.
The questions are semi-automatically generated using several question templates in order to train basic facts, more complex patterns, and connections between textbooks encoded in SNIK.

@@

This terminology is offered by SNIK~\citep{semantischesnetz,sniktec}, the Semantic Network of Information Management in Hospitals (\enquote{Krankenhaus} in German), which integrates knowledge extracted from three textbooks~\citep{bb,ob,he} and other sources such as interviews in the form of Linked Open Data.
In order to specify, which information should be extracted from the books and to facilitate comparisons, we use a common data model.

@@

\begin{figure}
\caption{The SNIK Quiz browser game available at \url{https://www.snik.eu/quiz}.}
\label{fig:snikquiz}
\centering
\includegraphics[width=0.6\textwidth]{img/snik-quiz.png}
\end{figure}

SNIK Quiz is designed as single-player game for English speaking students of Medical Informatics.
This group is diverse and includes students of Medicine, who may not have a background in Computer Science and Semantic Web technologies.
Target devices are PCs, tablets and smartphones, so multiple operating systems and input methods need to be supported.
Thus, SNIK Quiz is designed as an multiple choice quiz with at most four possible answers and published as an open source web application.
We employ an approach similar to Clover Quiz~\citep{cloverquiz}, which shows that Linked Data knowledge bases can be used to semi-automatically generate cross-domain multiple-choice questions on DBpedia~\citep{dbpedia}.
For each question (\emph{stem}), we generate a correct answer (\emph{key}) and one or more incorrect answers (\emph{distractors}).
The data is semi-automatically generated using SPARQL queries, such as \cref{lst:sparql}, on the public SPARQL endpoint of SNIK\footnote{\url{https://www.snik.eu/sparql}} followed by minimal postprocessing to achieve more natural looking questions.
The graph structure of SNIK allows the generation of difficult to guess distractors by using entities that are semantically close to the key, using path lengths of at most 2 in the graph.

%In order to specify, which information should be extracted from the books and to facilitate comparisons, we use a common data model.
%Because processed textbooks contain abstract knowledge instead of information about any specific hospital, all concepts are modelled as classes.
%We thus call our data model the \enquote{meta model} in accordance with the term's definition as a shared modelling language~\citep[p.~8]{ob}.
%The meta model (see \cref{fig:metamodel}) provides a common vocabulary for the domain of HIS management and thus defines, which superclasses and properties can be used.
%SNIK version \snikversionlink{} comprises five subontologies that are built upon the meta model, see Table 1.
%At the head of the class hierarchy (see \cref{fig:hierarchy}) is the \enquote{Top} class, which has exactly three disjunctive subclasses.
%At the head of the class hierarchy is the \enquote{Top} class, which has exactly three disjunctive subclasses.
%
%Following the meta model, each class has to be a subclass of exactly one of them.
%The correct superclass of a new concept can be found by answering the question: Who (\enquote{Role}) does what (\enquote{Function}) and which information (\enquote{EntityType}) is needed? If a concept is neither of them, it cannot be modeled using the meta model.
%As the subclass relation is transitive, a new class can be placed further down the hierarchy and it can still be inferred, whether it is a Function, Role or EntityType (see Figure 3).
%Besides the subclass relationship, two classes can be connected with relations provided by the meta model.
%The generic \enquote{is associated with} relationship carries little information.
%For example, a role and a function can be connected as \enquote{is involved in} \enquote{is responsible for} and \enquote{approves}.
%Relations that are neither of them can either be modeled by using the generic \enquote{is associated with} relation or by creating and using a new sub relation of \enquote{is associated with}
%
%As a concession to practicality, we express each geleral rule extracted from a textbook as a single triple using classes as subject and object, and a property of the meta model.
%For example, the rule "the CEO is involved in project reviews" is modelled as \enquote{\texttt{:Ceo} \aurl{meta}{isInvolvedIn} \texttt{:ProjectReview}.}, where \texttt{:Ceo} is a subclass of \aurl{meta}{Role} and \aurl{meta}{ProjectReview} is a subclass of \aurl{meta}{Function}.
%While an OWL restrictions using \aurl{owl}{someValuesFrom} and \aurl{owl}{allValuesFrom} would be technically correct, the knowledge is not expressed that specifically in the textbooks.
%Additionally, encoding each fact as a single triple facilitates tool support and prevents inconsistencies through non-atomic changes.

\section{Results}\label{sec:application}
The resulting question data is generated by several templates, as shown in \cref{tab:templates}, which are designed to either train basic facts, more complex patterns in one of the textbooks or connections between the different textbooks modelled in SNIK.

@@

  ?class (!(meta:subTopClass|rdf:type)){1,2} ?a1,?a2,?a3.
  owl:Class ^a ?a1,?a2,?a3.
  FILTER(?class!=?a1&&?class!=?a2&&?class!=?a3&&?a1<?a2&&?a2<?a3)

  ?a1 rdfs:label ?a1l. FILTER(LANGMATCHES(LANG(?a1l),"en"))
  ?a2 rdfs:label ?a2l. FILTER(LANGMATCHES(LANG(?a2l),"en"))
  ?a3 rdfs:label ?a3l. FILTER(LANGMATCHES(LANG(?a3l),"en"))
} GROUP BY ?class LIMIT 1000
\end{lstlisting}
%
%Due to the limited nesting capabilties of SPARQL, which does not support loops but only subqueries that cannot access variables declared outside their scope, querying for distinct sets of 4 neighbours, where exactly one was connected over a certain property to a certain object, was not possible with our Virtuoso SPARQL endpoint initially.
%We circumvented the timeout by calculating the neighbour-relation as a first step and uploading it to the endpoint.
%
%SNIK Quiz is freely available as an open source web application.

%The definition approach focuses on the question of which definition is fitting for a given term. 
%To increase the difficulty of the strategy, the distractors are chosen to be at most two vertices away from the edge which represents the correct term, much like in the label-definition-type.

\begin{figure}
\includegraphics[width=0.7\textwidth]{img/intertwined_cml.png} 
\caption{Left to right: correct answer, difficult and easy distractor for the \emph{intertwined} question type~\citep{snikquizba}.}
\label{fig:intertwined}
\end{figure}

%This question type tests the connection between a textbook about tactical information management~\cite{ob} and one about strategic information management~\cite{bb} based on the existing \aurl{skos}{closeMatch} interlinks.
%The aim is to help students transfer knowledge about one textbook to the other.
%The questions have the form: \emph{\enquote{In [Tactical / Strategic IM], the [subject] [predicate] the [object], while in [Strategic / Tactical IM], the [subject] [predicate] the [object].}} with two possible answers: true and false.
%Examplarly questions are given in \cref{tab:closematch}.

@@

\iffalse
\paragraph{occurence}
\begin{table}[h]
\begin{tabulary}{\textwidth}{LL}
\toprule
question	&correct\\
\midrule
In which contexts does the term \enquote{Automated Observation} occur?		&Tactical Information Management \\
In which contexts does the term \enquote{Health Insurance Company} occur?	&Strategic Information Management \\
In which contexts does the term \enquote{System Analysis} occur?			&Both Contexts \\
In which contexts does the term \enquote{System Administrator} occur?		&Neither\\
\bottomrule
\end{tabulary}
\caption{Exemplary \emph{occurrence}-questions and correct answers.}
\label{tab:occurence}
\end{table}

The \emph{occurence} question type is a specialization of \emph{closeMatch}, where the student has to choose whether a term occurs in~\cite{ob},~\cite{bb}, in both textbooks or neither of them.
Exemplary questions are given in \cref{tab:occurence}.
%mögliche Frage ist hier: \enquote{In which books does the term \emph{Chief Information Officer} occur?}.
The context of the questions can be augmented with the definitions of the concepts.
\fi

%The question types definition and subject were used to generate 1231 English questions, see \cref{tab:templates}.
The question types definition and subject were presented in a first prototype of SNIK Quiz to students of Medical Informatics from the Universities of Amsterdam, Heidelberg and Leipzig during the international Frank van Swieten lectures in 2019 and were positively received.
An extended version of SNIK Quiz including the query types definition, definitions, subject, intertwined, closeMatch and occurrence was rated by two experts of hospital information management and one student of Medical Informatics, see \cref{tab:eval}.
%The technical environment of SNIK is characterized in previous work [11].

@@

% transposed
\begin{table}[h]
\begin{tabularx}{\textwidth}{Xcccccc}
\toprule
			&definition		&definitions	&subject	&intertwined	&closeMatch	&occurence\\
\midrule
interview 1	&4					&3			&5--6		&7				&8			&7\\
interview 2	&6					&4			&7			&7--8			&7--8		&5\\
interview 3	&3					&3			&6			&8				&8			&7\\
\bottomrule
\end{tabularx}
\caption{Rating given by interviewees based on the subjective complexity of the questions on a scale between 1 and 10 with 10 representing maximum complexity~\citep{snikquizba}.}
\label{tab:eval}
\end{table}

\section{Discussion}
Similar to Clover Quiz~\citep{cloverquiz}, SNIK Quiz contains basic questions that refer to singular facts. 
These questions were received positively during the Frank van Swieten lectures and the evaluation ratings on subjective complexity show promising results.
A question template to test the understanding of relationships involving multiple facts has been successfully evaluated for middle school questions using an ontology of biology~\citep{multiplechoicequestion}, however the style of questions was deemed to be repetitive by two of the evaluating teachers.
%complex questions such as \enquote{What dissolves salt, has cohesion, and is an input to evaporation? (Water)}
SNIK Quiz employs a similar approach but uses several different question templates in order to achieve a more varied question style.

The main limitation of SNIK Quiz is that qualitative feedback on those complex questions is mixed.
One of the experts questioned the didactic value of the \emph{intertwined} questions, as the users cannot know the exact graph structure of SNIK and thus may difficulties deciding, which triplets of concepts are most strongly connected.
While the closeMatch were rated as most complex, the complexity was seen mostly seen as grammatical and not enough on the didactically relevant relationships between the entities.
Contrary to the initial assumption that well explained questions would be beneficial, shorter questions were preferred as they could be read more quickly.
%A limitation of the distractor generation using graph neighbourhood is that it includes subclass/superclass relationships, where it is not clear whether the given wrong answer can be argued to hold as well, even if that fact is not explicitly modelled.
Questions should also clarify that the least specific correct answer is expected in cases such as the example for the subject template in \cref{tab:templates}:
As a subclass of the correct answer \enquote{physician}, each \enquote{senior physician} is also implicitly responsible for medical admission and for \enquote{health care professionals} (superclass of physician) this is at least partly true.
As SNIK can only cover the domain of HIM as far as it is described by the underlying textbooks, distractors may actually be correct answers in the real world.
Evaluation of SNIK Quiz questions helps uncover and fix missing and incorrect facts in SNIK.
%Generally, close neighbourhood is problematic for distractor generation in SNIK because, .
%It needs to be investigated further, whether subclass relationships should be excluded in future work or whether provide valuable distractors.
% SeniorPhysician < Physician < HealthCareProfessional
%Distractor generation using graph neighbourhood suffers from the meta model of SNIK, where 
%Generally,

@@

%\section{Future Work}
\section{Conclusions}
SNIK Quiz shows that knowledge on the management of information systems in medicine and health care can be used to semi-automatically generate multiple-choice questions.
While preliminary evaluations show promising results, the complex question types need to be investigated further before it can be effectively used by students.
Future work should also include a quantitative evaluation of learning efficiency when supplementing courses with SNIK Quiz.
%Use of neural networks and language models in combination with linked data to generate more natural questions and answers is another avenue for further exploration.

>>>>

\begin{abstract}
SNIK is a knowledge base about the management of health information systems generated by extracting Linked Data from textbooks and other sources.
SNIK describes functions, roles executing these functions, and entity types, the information used or updated by these functions.
We present SNIK Quiz, a browser game in which students answer multiple-choice questions about information management in hospitals based on SNIK.
The questions are semi-automatically generated using templates in order to train basic facts, more complex patterns, and connections between textbooks encoded in SNIK.

@@

This terminology is offered by SNIK~\citep{semantischesnetz,sniktec}, the Semantic Network of Information Management in Hospitals (\enquote{Krankenhaus} in German), which integrates knowledge extracted from textbooks~\citep{bb,ob,he} and other sources such as interviews in the form of Linked Open Data.
In order to specify, which information should be extracted and to facilitate comparisons, we use a common data model.

@@

\begin{figure}
\caption{The SNIK Quiz browser game available at \url{https://www.snik.eu/quiz}.}
\label{fig:snikquiz}
\centering
\includegraphics[width=0.5\textwidth,trim={0 0 0 30mm},clip]{img/snik-quiz.png}
\end{figure}

SNIK Quiz is an English single-player game for students of Medical Informatics.
This group is diverse and includes students without a background in Semantic Web technologies.
Target devices are PCs, tablets and smartphones, so multiple operating systems and input methods need to be supported.
SNIK Quiz is designed as an multiple choice quiz with at most four possible answers and published as an open source web application.
We employ an approach similar to Clover Quiz~\citep{cloverquiz}, which shows that Linked Data knowledge bases can be used to semi-automatically generate cross-domain multiple-choice questions on DBpedia~\citep{dbpedia}.
For each question (\emph{stem}), we generate a correct answer (\emph{key}) and one or more incorrect answers (\emph{distractors}).
The data is semi-automatically generated using SPARQL queries on SNIK, such as \cref{lst:sparql}, followed by minimal postprocessing to achieve more natural looking questions.
%\footnote{\url{https://www.snik.eu/sparql}}
The graph structure of SNIK allows the generation of difficult distractors by using entities semantically close to the key, using path lengths of at most 2 in the graph.
Evaluation uses semi-structured interviews with standardized questions but partly open answers:
Expections for \enquote{good} simple and complex questions are asked.
Then, each question category is rated on a scale of 1 to 10.
Each question is commented based on the individual critieria of the first step.
Finally, the subjective influence is noted on:
length of the question and answers,
interconnectedness of the content and
semantic similarity of the key and distractors.
%In order to specify, which information should be extracted from the books and to facilitate comparisons, we use a common data model.
%Because processed textbooks contain abstract knowledge instead of information about any specific hospital, all concepts are modelled as classes.
%We thus call our data model the \enquote{meta model} in accordance with the term's definition as a shared modelling language~\citep[p.~8]{ob}.
%The meta model (see \cref{fig:metamodel}) provides a common vocabulary for the domain of HIS management and thus defines, which superclasses and properties can be used.
%SNIK version \snikversionlink{} comprises five subontologies that are built upon the meta model, see Table 1.
%At the head of the class hierarchy (see \cref{fig:hierarchy}) is the \enquote{Top} class, which has exactly three disjunctive subclasses.
%At the head of the class hierarchy is the \enquote{Top} class, which has exactly three disjunctive subclasses.
%Following the meta model, each class has to be a subclass of exactly one of them.
%The correct superclass of a new concept can be found by answering the question: Who (\enquote{Role}) does what (\enquote{Function}) and which information (\enquote{EntityType}) is needed? If a concept is neither of them, it cannot be modeled using the meta model.
%As the subclass relation is transitive, a new class can be placed further down the hierarchy and it can still be inferred, whether it is a Function, Role or EntityType (see Figure 3).
%Besides the subclass relationship, two classes can be connected with relations provided by the meta model.
%The generic \enquote{is associated with} relationship carries little information.
%For example, a role and a function can be connected as \enquote{is involved in} \enquote{is responsible for} and \enquote{approves}.
%Relations that are neither of them can either be modeled by using the generic \enquote{is associated with} relation or by creating and using a new sub relation of \enquote{is associated with}
%As a concession to practicality, we express each geleral rule extracted from a textbook as a single triple using classes as subject and object, and a property of the meta model.
%For example, the rule "the CEO is involved in project reviews" is modelled as \enquote{\texttt{:Ceo} \aurl{meta}{isInvolvedIn} \texttt{:ProjectReview}.}, where \texttt{:Ceo} is a subclass of \aurl{meta}{Role} and \aurl{meta}{ProjectReview} is a subclass of \aurl{meta}{Function}.
%While an OWL restrictions using \aurl{owl}{someValuesFrom} and \aurl{owl}{allValuesFrom} would be technically correct, the knowledge is not expressed that specifically in the textbooks.
%Additionally, encoding each fact as a single triple facilitates tool support and prevents inconsistencies through non-atomic changes.

\section{Results}\label{sec:application}
The resulting question data is generated by templates, see \cref{tab:templates}, which are designed to either train basic facts or more complex patterns.
%in one of the textbooks or connections between the different textbooks modelled in SNIK.

@@

  ?class (!(meta:subTopClass|rdf:type)){1,2} ?a1,?a2,?a3.
  owl:Class ^a ?a1,?a2,?a3.
  FILTER(?class!=?a1&&?class!=?a2&&?class!=?a3&&?a1<?a2&&?a2<?a3)
  ?a1 rdfs:label ?a1l. FILTER(LANGMATCHES(LANG(?a1l),"en"))
  ?a2 rdfs:label ?a2l. FILTER(LANGMATCHES(LANG(?a2l),"en"))
  ?a3 rdfs:label ?a3l. FILTER(LANGMATCHES(LANG(?a3l),"en"))
} GROUP BY ?class LIMIT 1000
\end{lstlisting}
%Due to the limited nesting capabilties of SPARQL, which does not support loops but only subqueries that cannot access variables declared outside their scope, querying for distinct sets of 4 neighbours, where exactly one was connected over a certain property to a certain object, was not possible with our Virtuoso SPARQL endpoint initially.
%We circumvented the timeout by calculating the neighbour-relation as a first step and uploading it to the endpoint.
%SNIK Quiz is freely available as an open source web application.
%The definition approach focuses on the question of which definition is fitting for a given term. 
%To increase the difficulty of the strategy, the distractors are chosen to be at most two vertices away from the edge which represents the correct term, much like in the label-definition-type.
\begin{figure}
\includegraphics[width=0.5\textwidth]{img/intertwined_cml.png} 
\caption{Left to right: correct answer, difficult and easy distractor for the \emph{intertwined} question type~\citep{snikquizba}.}
\label{fig:intertwined}
\end{figure}
%This question type tests the connection between a textbook about tactical information management~\cite{ob} and one about strategic information management~\cite{bb} based on the existing \aurl{skos}{closeMatch} interlinks.
%The aim is to help students transfer knowledge about one textbook to the other.
%The questions have the form: \emph{\enquote{In [Tactical / Strategic IM], the [subject] [predicate] the [object], while in [Strategic / Tactical IM], the [subject] [predicate] the [object].}} with two possible answers: true and false.
%Examplarly questions are given in \cref{tab:closematch}.

@@

\iffalse
\paragraph{occurence}
\begin{tabulary}{\textwidth}{LL}
question	&correct\\
In which contexts does the term \enquote{Automated Observation} occur?		&Tactical Information Management \\
In which contexts does the term \enquote{Health Insurance Company} occur?	&Strategic Information Management \\
In which contexts does the term \enquote{System Analysis} occur?			&Both Contexts \\
In which contexts does the term \enquote{System Administrator} occur?		&Neither\\
\caption{Exemplary \emph{occurrence}-questions and correct answers.}
\label{tab:occurence}
The \emph{occurence} question type is a specialization of \emph{closeMatch}, where the student has to choose whether a term occurs in~\cite{ob},~\cite{bb}, in both textbooks or neither of them.
Exemplary questions are given in \cref{tab:occurence}.
%mögliche Frage ist hier: \enquote{In which books does the term \emph{Chief Information Officer} occur?}.
The context of the questions can be augmented with the definitions of the concepts.
\fi
%The question types definition and subject were used to generate 1231 English questions, see \cref{tab:templates}.
The question types definition and subject were presented in a first prototype to students of Medical Informatics
%from the Universities of Amsterdam, Heidelberg and Leipzig
during the international Frank van Swieten lectures in 2019 and were positively received.
An extended version of SNIK Quiz including the query types definition, definitions, subject, intertwined, closeMatch and occurrence was rated by two experts of hospital information management and one student of Medical Informatics, see \cref{tab:eval}.
%The technical environment of SNIK is characterized in previous work [11].

@@

% transposed
\begin{table}[h]
\begin{tabularx}{\textwidth}{Xcccccc}
\toprule
			&definition		&definitions	&subject	&intertwined	&closeMatch	&occurence\\
\midrule
interview 1	&4					&3			&5--6		&7				&8			&7\\
interview 2	&6					&4			&7			&7--8			&7--8		&5\\
interview 3	&3					&3			&6			&8				&8			&7\\
\bottomrule
\end{tabularx}
\caption{Interviewee rating on subjective complexity of the questions on a scale between 1 and 10 ~\citep{snikquizba}.}
\label{tab:eval}
\end{table}

\section{Discussion}
Like Clover Quiz~\citep{cloverquiz}, SNIK Quiz contains basic questions that refer to singular facts. 
These questions were received positively during the Frank van Swieten lectures and the evaluation ratings on subjective complexity show promising results.
Questions that test the understanding of relationships involving multiple facts have been successfully evaluated for middle school questions using an ontology of biology~\citep{multiplechoicequestion}, however the style of questions was deemed to be repetitive by two of the evaluating teachers.
%complex questions such as \enquote{What dissolves salt, has cohesion, and is an input to evaporation? (Water)}
SNIK Quiz uses multiple templates in order to achieve a more varied question style.
A limitation of SNIK Quiz is that qualitative feedback on complex questions is mixed.
One of the experts questioned the didactic value of the \emph{intertwined} questions, as the users cannot know the exact graph structure of SNIK and thus may have difficulties deciding, which triplets of concepts are most strongly connected.
While the complexity of closeMatch was rated the highest, it was seen as mostly grammatical rather then caused by relationships between entities.
Contrary to the initial assumption, shorter questions were preferred as they could be read more quickly.
%A limitation of the distractor generation using graph neighbourhood is that it includes subclass/superclass relationships, where it is not clear whether the given wrong answer can be argued to hold as well, even if that fact is not explicitly modelled.
Questions should also clarify that the least specific correct answer is expected in cases such as the example for the subject template in \cref{tab:templates}:
As a subclass of the correct answer \enquote{physician}, each \enquote{senior physician} is also implicitly responsible for medical admission and for \enquote{health care professionals} (superclass of physician) this is at least partly true.
As SNIK can only cover the domain of HIM as described by the underlying textbooks, distractors may actually be correct answers in the real world.
%Generally, close neighbourhood is problematic for distractor generation in SNIK because, .
%It needs to be investigated further, whether subclass relationships should be excluded in future work or whether provide valuable distractors.
% SeniorPhysician < Physician < HealthCareProfessional
%Distractor generation using graph neighbourhood suffers from the meta model of SNIK, where 
%Generally,

@@

%\section{Future Work}
\section{Conclusions}
SNIK Quiz shows that HIM knowledge can be used to semi-automatically generate multiple-choice questions.
Analysing questions also helps to uncover and fix missing and incorrect facts in SNIK.
While preliminary evaluations show promising results, complex question types need to be investigated further.
%before it can be effectively used by students.
Future work should also include a quantitative evaluation of learning efficiency when supplementing courses with SNIK Quiz.
%Use of neural networks and language models in combination with linked data to generate more natural questions and answers is another avenue for further exploration.
